Numerical investigation of viscous flow instabilities through heterogeneous porous media. Advantages and limitations of unstructured and adaptive meshes in 2D and 3D domains under different mobility scenarios.

### 2017-08-22 Papers/ViscousInstabilities/article_figure2.tex
kostas speed up do not rush

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) flow at t=250 (fixed mesh)  
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) flow at t=250 (adaptive mesh)    
}
}     
\caption{For $t=0.125$s, $2$ test-cases under the VR=$10$ and under fixed (top) and adaptive(bottom) mesh are compared. There is a significant difference on the main front (left hand side of the domain) and the number of finger that appear.}
\label{fig:2testcase_a}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) flow at t=500 (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) flow at t=500 (adaptive mesh)     
}
}     
\caption{At $t=0.25$s ($t=500$, timestemp) cross flow is taking place at the upper part of the formation. The fingers start to becoming more proufound as can been seen at the bottom.}
\label{fig:2testcase_b}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) flow at t=1500 (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) flow at t=1500 (adaptive mesh)     
}
}     
\caption{At $t=0.75 sec$ ($t=1500$, timestemp) the initial cross flow is now fully developed and has travel all the way towards the outlet (right-hand side). and the finger below start forming a front that is also travelling towards the left-hand side.}
\label{fig:2testcase_c}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) flow at t=end (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) flow at t=end (adaptive mesh)     
}
}     
\caption{Using the $P_{1}DGP_{2}$ element type for VR=$10$ under the same time steps, we compared the impact of fixed and adaptive mesh for the same timeframe. The end of simulation happens at $time=5 sec$ and for the timestemp $t=9999$ while the number of elements in both simulations was approximately $4700$. When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
\label{fig:2testcase_d}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
  \includegraphics[width=.67\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) double inlet adaptive mesh   
}
}     
\caption{Comparing test-cases of fixed and adaptive mesh while a second region/inlet is introduced. For $t=0.101$s, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps. For this simulation there are $13226$ elements for the fixed messh and $43716$ for the adaptive.}
\label{fig:3testcase_a}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.9\textwidth]{./Pics1/5reg_dinlet_adapt_500_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) double inlet adaptive mesh   
}
}     
\caption{For $t=5$s there is a comparison between fixed mesh(a) and adaptive mesh(b).}
\label{fig:3testcase_b}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/5reg_dinlet_fixed_1500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.9\textwidth]{./Pics1/5reg_dinlet_adapt_1500_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) double inlet adaptive mesh   
}
}     
\caption{For $t=7.5$s this is a comparison between fixed mesh(a) and adaptive mesh(b).}
\label{fig:3testcase_c}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/5reg_dinlet_fixed_end.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.9\textwidth]{./Pics1/5reg_dinlet_adapt_end_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) double inlet adaptive mesh   
}
}     
\caption{This is a comparison between fixed mesh(a) and adaptive mesh(b) at the end of the simulation. For the fixed mesh at this point the maximum number of point is $13226$ while for the adaptive mesh is $7582$ and most of them are located where is needed in the domain.}
\label{fig:3testcase_d}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.93\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{4.0cm} (a) fixed and unstructured mesh for VR = 100 (start)   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.7\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{3.75cm} (b) fixed and unstructured mesh for VR = 100 (t = 1500)   
}
}     
\caption{For the case of VR=$100$ from top to bottom, the number of elements is $4680$ and fixed and unstructured mesh was used for the same time steps, t=$0.25$s or t=500(a), t=$0.75$s or t=1500(b). }
\label{fig:4testcase_a}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.7\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{3.75cm} (c) fixed and unstructured mesh for VR = 100    
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.93\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{7.cm} (d) end of simulations     
}
}     
\caption{screenshot (c) is for t=$1.5$s or t=$3000$ and screenshot (d) is for t=$3.175$s, at the end of the simulations. }
\label{fig:4testcase_b}
\end{figure}
\end{landscape}
\clearpage

%%%
%%% FIGURE XXXXXX
%%%
\begin{figure}[ht]
\vbox{\vspace{-.5cm}
      \hbox{\includegraphics[width=\textwidth]{./Pics1/3D_Channel/Test_SlowNew_MeshPermeability.pdf} }
      \hbox{\hspace{5.0cm} (a) permeability map }}
\caption{3D channel flow. The domain contains 243056 \PN[1]{1} element-pairs.}
\label{fig:3DChannel_PermMesh}
\end{figure}
\clearpage

%%%%
%%%%  FIGURE
%%%%
%\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_100_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{10.0cm} (a)     
}
\hbox{\hspace{3.5cm}
\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_490_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{10.cm} (b)      
}
}     
\caption{Contours of Darcy velocity in XY and YZ planes for (a) t=$0.91$s and (b)t=$4.3$s.}
\label{fig:3DChannel_darcy_vel}
\end{figure}
%\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_sat_100.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{10.0cm} (a)     
}
\hbox{\hspace{3.5cm}
\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_sat_490.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{10.cm} (b)      
}
}     
\caption{For the same time steps as in fig.\ref{fig:3DChannel_darcy_vel} there is a description of the saturation front in (a) t=$0.91$s and (b)t=$4.3$s.}
\label{fig:3DChannel_sat}
\end{figure}
\end{landscape}
\clearpage

%%%
%%% FIGURE XXXXXX
%%%
\begin{landscape}
  \begin{figure}[ht]
  \vbox{\vspace{-.5cm}
      \hbox{\includegraphics[width=.55\textwidth, height=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D30c} 
            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D60c}
            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D90c} }
      \hbox{\hspace{2.0cm} (a) t=0.29s \hspace{6.cm} (b) t=0.56s \hspace{4.cm} (c) t=0.82s}
      \vspace{0.5cm}
      \hbox{\hspace{.5cm} \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D110c}
            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D150c}
            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D400c} }
      \hbox{\hspace{3.cm} (d) t=1.00s \hspace{3.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s }}
\caption{XXX.}
\label{fig:3DChannel_Isosurf}
\end{figure}
\end{landscape}
\clearpage

>>>>

%%%
%%% FIGURE XXXXXX
%%%
\begin{figure}[ht]
\vbox{\vspace{-.5cm}
      \hbox{\includegraphics[width=\textwidth]{./Pics1/3D_Channel/Test_SlowNew_MeshPermeability.pdf} }}
\caption{3D channel flow: permeability distribution. The domain contains 243056 \PN[1]{1} element-pairs.}
\label{fig:3DChannel_PermMesh}
\end{figure}
\clearpage

%%%%
%%%%  FIGURE
%%%%
%\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{0.5cm}
\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_30_1.pdf} 
}
\vspace{-12.0cm}
\hbox{\hspace{6.0cm} (a)     
}
\hbox{\hspace{0.5cm}
\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_490_1.pdf}
}
\vspace{-12.0cm}
\hbox{\hspace{6.0cm} (b)      
}
}     
\caption{3D channel flow: XY and YZ planes showing wetting fluid phase Darcy velocity vectors overlapped with wetting fluid saturation at (a) t=$0.29$s and (b)t=$4.3$s. \red{(AS I MENTIONED BEFORE THE FIGURE SHOULD SHOW OVERLAPPING VELOCITY VECTORS ON FLUID SATURATION FIELD INSTEAD OF OVERLAPPING VELOCITY VECTORS ON VELOCITY FIELD!!!! PLEASE CHANGE IT!! }}
\label{fig:3DChannel_planes}
\end{figure}
%\end{landscape}
\clearpage

\begin{comment}
%%%%
%%%%  FIGURE
%%%%
%\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\vspace{-5.0cm}
\includegraphics[width=0.75\textwidth]{./Pics1/3D_Channel/3D_channel_sat_30.pdf}
\includegraphics[width=0.75\textwidth]{./Pics1/3D_Channel/3D_channel_sat_100.pdf} 
}
\hspace{-5.0cm}
\hbox{\hspace{6.0cm} (a) \hspace{6.cm} (b)    
}
\hbox{\vspace{0.0cm}
\includegraphics[width=0.75\textwidth]{./Pics1/3D_Channel/3D_channel_sat_150.pdf}
\includegraphics[width=0.75\textwidth]{./Pics1/3D_Channel/3D_channel_sat_490.pdf}
}
\hspace{-5.0cm}
\hbox{\hspace{6.0cm} (c) \hspace{6.cm} (d)     
}
}     
\caption{The figures (a) t=$0.91$s and (b)t=$4.3$s give a description of the saturation front. }
\label{fig:3DChannel_sat}
\end{figure}
%\end{landscape}
\clearpage
\end{comment}

%%%
%%% FIGURE XXXXXX
%%%
\begin{landscape}
\begin{figure}[ht]
  \vbox{\vspace{-.5cm}
      \hbox{\includegraphics[width=.6\textwidth]{./Pics1/3D_Channel/3D_channel_sat_30.pdf} 
            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_60.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_90.pdf} } 
      \hbox{\hspace{2.cm} (a) t=0.29s \hspace{5.cm} (b) t=0.56s \hspace{4.cm} (c) t=0.82s}
      \vspace{0.5cm}
      \hbox{\hspace{.5cm} 
            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_110.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_150.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_490.pdf} }
      \hbox{\hspace{2.cm} (d) t=1.00s \hspace{5.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s  } }
\caption{3D channel flow: saturation front evolving in time and space with preferential flow pathways through 3.50 seconds of numerical simulations. Preferential flow pathway can be readily noticed in these frames, mirroring permeability distribution. The domain contains 368513 \PN[1]{1} elements.}
\label{fig:3DChannel_sat}
\end{figure}
\end{landscape}
\clearpage

%%%
%%% FIGURE XXXXXX
%%%
\begin{landscape}
  \begin{figure}[ht]
  \vbox{\vspace{-.5cm}
      \hbox{\includegraphics[width=.55\textwidth, height=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D30c.pdf} 
            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D60c.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D90c.pdf} }
      \hbox{\hspace{2.0cm} (a) t=0.29s \hspace{6.cm} (b) t=0.56s \hspace{4.cm} (c) t=0.82s}
      \vspace{0.5cm}
      \hbox{\hspace{.5cm} \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D110c.pdf}
            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D150c.pdf}
            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D400c.pdf} }
      \hbox{\hspace{3.cm} (d) t=1.00s \hspace{3.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s }}
\caption{3D channel flow: Isosurfaces for wetted phase saturatioh ranging from 0.45 and 0.60 at the same instants of time of Fig.~\ref{fig:3DChannel_sat}. Preferential flow pathway can be readily noticed in (b) and (f). Fingers' formation and growth can be clearly noticed in (b)-(e). The domain contains 368513 \PN[1]{1} elements.}
\label{fig:3DChannel_Isosurf}
\end{figure}
\end{landscape}
\clearpage

%%%
%%% FIGURE XXXXXX
%%%
\begin{landscape}
  \begin{figure}[ht]
  \vbox{\vspace{-.5cm}
      \hbox{\includegraphics[width=.5\textwidth, height=.45\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_30.pdf} 
            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_60.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_90.pdf} }
      \hbox{\hspace{3.0cm} (a) t=0.29s \hspace{4.cm} (b) t=0.56s \hspace{4.cm} (c) t=0.82s}
      \vspace{1.5cm}
      \hbox{\hspace{.5cm} \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_110.pdf}
            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_150.pdf}
            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_288.pdf} }
      \hbox{\hspace{3.cm} (d) t=1.00s \hspace{3.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s }}
\caption{For the same time steps as these are shown in figure \ref{fig:3DChannel_sat} there is a description of the same flow path but now using an adaptive and unstructured mesh. The aim was to describe in greater detail the finger patterns, as the flow develops but also address the importance of a resolution, in this case the type of mesh that is used to capture these phenomena.}
\label{fig:3DChannel_sat_adapt}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
%\begin{landscape}
\begin{figure}[ht] 
\vbox{\vspace{-3.5cm}
\vbox{\hspace{2.5cm}
\includegraphics[width=0.75\textwidth]{./Pics1/3D_Channel/3D_channel_sat_end.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{2.0cm} (a) fixed unstructured mesh of 322493 elements    
}
\hbox{\hspace{2.5cm}
\includegraphics[width=0.75\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_end.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{-2.0cm} (b) adaptive and unstructured mesh with a maximum of 1242202 elements at the end of the simulation    
}
}     
\caption{This is a qualitative comparison at t=end of simulation, for bot the fixed and unstructured mesh used in the 3D domain. \red{perhaps we need to change the order between this figure and the \ref{fig:3DChannel_sat_adapt}? } }
\end{figure}
%\end{landscape}
\clearpage
